The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-02 src/ms.tex
words about user communities

  \item[Understanding, communicating with, and engaging our user communities] Different overlapping and intersecting communities of users: telescopes, archives, researchers, students, educators, general public. Communities have different needs from Astropy. Also, as ecosystem grows, making sure users know about all of the functionality (workshops, tutorials, educational materials, discoverability, accessibility) (Continued engagement with user community).

>>>>

  \item[Understanding, communicating with, and engaging our user communities]
  The \astropy Project is used by a number of intersecting and overlapping
  communities, such as telescope operations and data management, data archives,
  researchers, students, educators, and the general public.
  These communities have different needs from and uses for \astropy, many of
  which we are only aware of through individual engagement from members of these
  respective communities.
  This kind of communication may provide bias pespectives on these communities.
  We therefore need to develop more formal ways of engaging these communities in
  more democratic ways, such as through running and analyzing user surveys, or
  creating and engaging with user groups that can better represent these
  communities.
  Additionally, as the \astropy ecosystem has and continues to grow, we need to
  ensure that users in these different communities have access to educational
  materials to train new users to use \astropy and \python software tools.
  This may involve tailoring workshops, tutorials, and educational materials to
  these communities, however this represents a significant maintenance and
  content-development burden on the Project.
